---
title: "LCSC"
author: "Arun Kumar"
date: "2023-06-07"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 



```{r }
library(tidyverse)
library(readxl)

```

## SPFA_Data
# Reda SPFA Data sheet from excle sheet1

```{r, echo=FALSE}
raw_data <- read_excel("data/DEGs in SP FA _CD133+FA_EpCAM+FA _1_(Autosaved).xlsx", sheet = 1)
```
# select the data column
```{r}
raw_sub <- raw_data %>% 
  select(.,`Gene symbol`,Log2FoldChange,`-log(P-value)`,`FDR DOWN`)

```

# filter the data on criteria 
# log2fold between (0.6 to -0.6)
# -log(p-value) between (2 to -2)
# FDRdown < 0.05

## SPFA DEGs (all)
```{r}

 All_DEGs_SPFA <- subset(raw_sub, (Log2FoldChange > 0.6 | Log2FoldChange < -0.6) & (`-log(P-value)` > 2 | `-log(P-value)` < -2) & `FDR DOWN`< 0.05)
write.csv(All_DEGs_SPFA,"SP NSP Up_Dn DEGs/1.All_DEGs_SPFA.csv")
```

# SP FA up Regulated DEGs > 0.6 log2foldchange
```{r}
spfA_upregulated_DEGs <- subset(All_DEGs_SPFA, (Log2FoldChange > 0.6))

## calculate fold change and add the column in data frame.
Fold_Change <- 2^spfA_upregulated_DEGs$Log2FoldChange

spfA_upregulated_DEGs_FC <- cbind(spfA_upregulated_DEGs, FoldChange = Fold_Change)

write.csv(spfA_upregulated_DEGs_FC,"SP NSP Up_Dn DEGs/2.spfA_upreg_DEGs_FC.csv")
```

## SPFA Down Regulated DEGs < 0.6 log2foldchange

```{r}
spfA_downregulated_DEGs <- subset(All_DEGs_SPFA, (Log2FoldChange < 0.6))
## calculate fold change and add the column in data frame.
Fold_Change <- 2^spfA_downregulated_DEGs$Log2FoldChange

spfA_downregulated_DEGs_FC <- cbind(spfA_downregulated_DEGs, FoldChange = Fold_Change)

write.csv(spfA_downregulated_DEGs_FC,"SP NSP Up_Dn DEGs/3.spfA_downreg_DEGs_FC.csv")
```


### NSP FA Data
# Reda SPFA Data sheet from excle sheet 5


```{r}
 raw_data_NSPFA <- read_excel("data/DEGs in SP FA _CD133+FA_EpCAM+FA _1_(Autosaved).xlsx", sheet = 5)
```

# select the data column
```{r}
raw_sub_NSPFA <-  raw_data_NSPFA %>% 
  select(.,`Gene symbol`,Log2FoldChange,`-log(P-value)`,`FDR DOWN`)
```

# filter the data on criteria 
#log2fold between (0.6 to -0.6)
# -log(p-value) between (2 to -2)
# FDRdown < 0.05


# All NSPFA DEGs
```{r}
All_DEGS_NSPFA <- subset(raw_sub_NSPFA, (Log2FoldChange > 0.6 | Log2FoldChange < -0.6) & (`-log(P-value)` > 2 | `-log(P-value)` < -2) & `FDR DOWN`< 0.05)

write.csv(All_DEGS_NSPFA,"SP NSP Up_Dn DEGs/4.All_DEGS_NSPFA.csv")
```

# NSPFA up Regulated DEGs > 0.6 log2foldchange

```{r}
nspfA_upregulated_DEGs <- subset(All_DEGS_NSPFA, (Log2FoldChange > 0.6))
## calculate fold change and add the column in data frame.
Fold_Change <- 2^nspfA_upregulated_DEGs$Log2FoldChange

nspfA_upregulated_DEGs_FC <- cbind(nspfA_upregulated_DEGs, FoldChange = Fold_Change)

write.csv(nspfA_upregulated_DEGs_FC,"SP NSP Up_Dn DEGs/5.nspfA_upreg_DEGs_FC.csv")
```

# NSPFA up Regulated DEGs < 0.6 log2foldchange
```{r}
nspfA_downregulated_DEGs <- subset(All_DEGS_NSPFA, (Log2FoldChange < 0.6))
## calculate fold change and add the column in data frame.
Fold_Change <- 2^nspfA_downregulated_DEGs$Log2FoldChange

nspfA_downregulated_DEGs_FC <- cbind(nspfA_downregulated_DEGs, FoldChange = Fold_Change)

write.csv(nspfA_downregulated_DEGs_FC,"SP NSP Up_Dn DEGs/6.nspfA_Dnreg_DEGs_FC.csv")
```

## CD133+FA_Data
# Read CD133+FA Data sheet from excle sheet 2

```{r}
raw_data_CD133PFA <- read_excel("data/DEGs in SP FA _CD133+FA_EpCAM+FA _1_(Autosaved).xlsx", sheet = 2)
# select the data column
raw_sub_CD133PFA <-  raw_data_CD133PFA %>% 
  select(.,`Gene symbol`,Log2FoldChange,`-log(P-value)`,`FDR DOWN`)

```

# filter the data on criteria 
#log2fold between (0.6 to -0.6)
# -log(p-value) between (2 to -2)
# FDRdown < 0.05


# All CD133+FA DEGs

```{r}
All_DEGS_CD133PFA <- subset(raw_sub_CD133PFA, (Log2FoldChange > 0.6 | Log2FoldChange < -0.6) & (`-log(P-value)` > 2 | `-log(P-value)` < -2) & `FDR DOWN`< 0.05)

write.csv(All_DEGS_CD133PFA,"SP NSP Up_Dn DEGs/7.All_DEGS_CD133PFA.csv")
```

# CD133PFA up Regulated DEGs > 0.6 log2foldchange

```{r}
CD133PFA_upregulated_DEGs <- subset(All_DEGS_CD133PFA, (Log2FoldChange > 0.6))
## calculate fold change and add the column in data frame.
Fold_Change <- 2^CD133PFA_upregulated_DEGs$Log2FoldChange

CD133PFA_upregulated_DEGs_FC <- cbind(CD133PFA_upregulated_DEGs, FoldChange = Fold_Change)

write.csv(CD133PFA_upregulated_DEGs_FC,"SP NSP Up_Dn DEGs/8.CD133PFA_upregulated_DEGs_FC.csv")
```

# CD133PFA Down Regulated DEGs < 0.6 log2foldchange

```{r}
CD133PFA_downregulated_DEGs <- subset(All_DEGS_CD133PFA, (Log2FoldChange < 0.6))
## calculate fold change and add the column in data frame.
Fold_Change <- 2^CD133PFA_downregulated_DEGs$Log2FoldChange

CD133PFA_downregulated_DEGs_FC <- cbind(CD133PFA_downregulated_DEGs, FoldChange = Fold_Change)

write.csv(CD133PFA_downregulated_DEGs_FC,"SP NSP Up_Dn DEGs/9.CD133PFA_downregulated_DEGs_FC.csv")
```

## CD133-FA_Data
# Read CD133-FA Data sheet from excle sheet 6

```{r}
raw_data_CD133NFA <- read_excel("data/DEGs in SP FA _CD133+FA_EpCAM+FA _1_(Autosaved).xlsx", sheet = 6)
# select the data column
raw_sub_CD133NFA <-  raw_data_CD133NFA %>% 
  select(.,`Gene symbol`,Log2FoldChange,`-log(P-value)`,`FDR DOWN`)
```

# filter the data on criteria 
#log2fold between (0.6 to -0.6)
# -log(p-value) between (2 to -2)
# FDRdown < 0.05


# All CD133-FA DEGs

```{r}
All_DEGS_CD133NFA <- subset(raw_sub_CD133NFA, (Log2FoldChange > 0.6 | Log2FoldChange < -0.6) & (`-log(P-value)` > 2 | `-log(P-value)` < -2) & `FDR DOWN`< 0.05)

write.csv(All_DEGS_CD133NFA,"SP NSP Up_Dn DEGs/10.All_DEGS_CD133NFA.csv")
```

# CD133NFA up Regulated DEGs > 0.6 log2foldchange

```{r}
CD133NFA_upregulated_DEGs <- subset(All_DEGS_CD133NFA , (Log2FoldChange > 0.6))
## calculate fold change and add the column in data frame.
Fold_Change <- 2^CD133NFA_upregulated_DEGs$Log2FoldChange

CD133NFA_upregulated_DEGs_FC <- cbind(CD133NFA_upregulated_DEGs, FoldChange = Fold_Change)

write.csv(CD133NFA_upregulated_DEGs_FC,"SP NSP Up_Dn DEGs/11.CD133NFA_upregulated_DEGs_FC.csv")
```

# CD133NFA down Regulated DEGs < 0.6 log2foldchange

```{r}

CD133NFA_downregulated_DEGs <- subset(All_DEGS_CD133NFA , (Log2FoldChange < 0.6))
## calculate fold change and add the column in data frame.
Fold_Change <- 2^CD133NFA_downregulated_DEGs$Log2FoldChange

CD133NFA_downregulated_DEGs_FC <- cbind(CD133NFA_downregulated_DEGs, FoldChange = Fold_Change)

write.csv(CD133NFA_downregulated_DEGs_FC,"SP NSP Up_Dn DEGs/12.CD133NFA_downregulated_DEGs_FC.csv")

```

## EpCAM+FA_Data
# Read EpCAM+FA_Data sheet from excle sheet 3

```{r}
raw_data_EpCAMPFA <- read_excel("data/DEGs in SP FA _CD133+FA_EpCAM+FA _1_(Autosaved).xlsx", sheet = 3)
# select the data column
raw_sub_EpCAMPFA <-  raw_data_EpCAMPFA %>% 
  select(.,`Gene symbol`,Log2FoldChange,`-log(P-value)`,`FDR DOWN`)
```

```{r}
All_DEGS_EpCAMPFA <- subset(raw_sub_EpCAMPFA , (Log2FoldChange > 0.6 | Log2FoldChange < -0.6) & (`-log(P-value)` > 2 | `-log(P-value)` < -2) & `FDR DOWN`< 0.05)

write.csv(All_DEGS_CD133NFA,"SP NSP Up_Dn DEGs/13.All_DEGS_EpCAMPFA.csv")
```

# EpCAM+FA up Regulated DEGs > 0.6 log2foldchange


```{r}

EpCAMPFA_upregulated_DEGs <- subset(All_DEGS_EpCAMPFA , (Log2FoldChange > 0.6))
## calculate fold change and add the column in data frame.
Fold_Change <- 2^EpCAMPFA_upregulated_DEGs$Log2FoldChange

EpCAMPFA_upregulated_DEGs_FC <- cbind(EpCAMPFA_upregulated_DEGs, FoldChange = Fold_Change)

write.csv(EpCAMPFA_upregulated_DEGs_FC,"SP NSP Up_Dn DEGs/14.EpCAMPFA_upreg_DEGs_FC.csv")
```

# EpCAM+FA DownRegulated DEGs < 0.6 log2foldchange


```{r}

EpCAMPFA_downregulated_DEGs <- subset(All_DEGS_EpCAMPFA , (Log2FoldChange < 0.6))
## calculate fold change and add the column in data frame.
Fold_Change <- 2^EpCAMPFA_downregulated_DEGs$Log2FoldChange

EpCAMPFA_downregulated_DEGs_FC <- cbind(EpCAMPFA_downregulated_DEGs, FoldChange = Fold_Change)

write.csv(EpCAMPFA_downregulated_DEGs_FC,"SP NSP Up_Dn DEGs/15.EpCAMPFA_downregulated_DEGs_FC.csv")

```

##EpCAM-FA_Data 
# Read EpCAM-FA_Data Data sheet from excle sheet 7


```{r}

raw_data_EpCAMNFA <- read_excel("data/DEGs in SP FA _CD133+FA_EpCAM+FA _1_(Autosaved).xlsx", sheet = 7)
# select the data column
raw_sub_EpCAMNFA <-  raw_data_EpCAMNFA %>% 
  select(.,`Gene symbol`,Log2FoldChange,`-log(P-value)`,`FDR DOWN`)

```

#

```{r}

All_DEGS_EpCAMNFA <- subset(raw_sub_EpCAMNFA , (Log2FoldChange > 0.6 | Log2FoldChange < -0.6) & (`-log(P-value)` > 2 | `-log(P-value)` < -2) & `FDR DOWN`< 0.05)

write.csv(All_DEGS_EpCAMNFA,"SP NSP Up_Dn DEGs/16.All_DEGS_EpCAMNFA.csv")
```

# EpCAM-FA up Regulated DEGs > 0.6 log2foldchange

```{r}

EpCAMNFA_upregulated_DEGs <- subset(All_DEGS_EpCAMNFA , (Log2FoldChange > 0.6))
## calculate fold change and add the column in data frame.
Fold_Change <- 2^EpCAMNFA_upregulated_DEGs$Log2FoldChange

EpCAMNFA_upregulated_DEGs_FC <- cbind(EpCAMNFA_upregulated_DEGs, FoldChange = Fold_Change)

write.csv(EpCAMNFA_upregulated_DEGs_FC,"SP NSP Up_Dn DEGs/17.EpCAMNFA_upregulated_DEGs_FC.csv")
```

##EpCAM-FA DownRegulated DEGs < 0.6 log2foldchange

```{r}


EpCAMNFA_downregulated_DEGs <- subset(All_DEGS_EpCAMNFA , (Log2FoldChange < 0.6))
## calculate fold change and add the column in data frame.
Fold_Change <- 2^EpCAMNFA_downregulated_DEGs$Log2FoldChange

EpCAMNFA_downregulated_DEGs_FC <- cbind(EpCAMNFA_downregulated_DEGs, FoldChange = Fold_Change)

write.csv(EpCAMNFA_downregulated_DEGs_FC,"SP NSP Up_Dn DEGs/18.EpCAMNFA_downregulated_DEGs_FC.csv")
```






